---
title: "Missingness 2 Coverage"
author: Anthony Pompetti
date: "2023-04-10"
date-format: long
cache: true
format: 
    html: 
        theme: darkly
        embed-resources: true
highlight-style: arrow-dark
---

```{r setup, echo=FALSE, cache=TRUE, cache.lazy=FALSE}
#| caption: "Loading libraries"
#| output: false
#| warning: false
source(here::here("scripts", "01_data_preprocessing.R"))
meth_raw_filter_75 <- readRDS(here("results","rds","meth_raw_filter_2.rds"))
sample_missing <- DelayedMatrixStats::colSums2(is.na(meth_raw_filter_75))
cpg_missing <- DelayedMatrixStats::rowSums2(is.na(meth_raw_filter_75))
```
## The data listed below reflect the methylation matrix after filtering for:

-   Filtered for coverage (loci kept if at least 2 samples had coverage
    \> 10)
-   Filtered for variance (row variance calculated, ordered rows by
    decreasing variance, kept top 50%)
-   Filtered samples that had \> 90% NA's (liv_4402)

## Number of CpGs in entire matrix:

```{r, cache=TRUE, echo=FALSE}
nrow(meth_raw_filter_75)
```

## Complete cases in matrix:

```{r, cache=TRUE, echo=FALSE}
nrow(meth_raw_filter_75) - sum(DelayedMatrixStats::rowAnyNAs(meth_raw_filter_75))
```

## % missingness of entire matrix:

```{r, cache=TRUE, echo=FALSE}
sum(is.na(meth_raw_filter_75))/length(meth_raw_filter_75) * 100
```

## When calculating missingness per sample,

```{r, echo=FALSE}
quantile(sample_missing)
```

## Distribution of missingness by samples

```{r, echo=FALSE}
hist(sample_missing,col = 'skyblue', main = '')
```

## Box plot of missingness by sample

```{r, echo=FALSE}
boxplot(sample_missing, col = 'skyblue')
```

## When calculating missingness per CpG,

```{r, echo=FALSE}
quantile(cpg_missing)
```

## Distribution of missingness by CpGs

```{r, echo=FALSE}
hist(cpg_missing,col = 'skyblue', main = '')
```

## Box plot of missingness by CpGs

```{r, echo=FALSE}
boxplot(cpg_missing,col = 'skyblue')
```