---
title: "PCA Plots"
author: Anthony Pompetti
date: "2023-02-15"
date-format: long
format: 
    html: 
        theme: darkly
        embed-resources: true
highlight-style: arrow-dark
editor_options: 
  chunk_output_type: console
---
```{r setup, echo=FALSE}
#| caption: "Loading libraries"
#| output: false
#| warning: false
source(here::here("scripts", "01_data_preprocessing.R"))
```

```{css, echo=FALSE}
.panel-tabset {
  font-size: 20px;
}
```
## Complete Cases All samples (without liv_4402)
::: {.panel-tabset}
## Organ (PC1,PC2)
```{r, cache=TRUE, echo=FALSE}
pca <- trqwe::mcreadRDS(here::here("results","rds","PCA","pca_75_all_cc.rds"), mc.cores = 4)
pc_scores <- pca$rotated %>% as.data.frame
pc_scores$microbiome <- pca$metadata$microbiome
pc_scores$age <- pca$metadata$age
pc_scores$organ <- pca$metadata$organ
pc_scores$batch <- pca$metadata$batch
pc_scores$strain <-  pca$metadata$strain
p <- ggplot(pc_scores, aes(x = PC1, y = PC2, color = organ, shape = strain, text = rownames(pc_scores))) +
geom_point() +
labs(title = "PCA Plot") +
xlab(str_glue("PC1, {round(pca$variance[1],2)}%")) +
ylab(str_glue("PC2, {round(pca$variance[2],2)}%")) +
theme(plot.title = element_text(size = 20))

ggplotly(p, tooltip = "text")
```
## Organ (PC2,PC3)
```{r, cache=TRUE, echo=FALSE}
p <- ggplot(pc_scores, aes(x = PC2, y = PC3, color = organ, shape = strain, text = rownames(pc_scores))) +
geom_point() +
labs(title = "PCA Plot") +
xlab(str_glue("PC2, {round(pca$variance[2],2)}%")) +
ylab(str_glue("PC3, {round(pca$variance[3],2)}%")) +
theme(plot.title = element_text(size = 20))

ggplotly(p, tooltip = "text")
```
## Microbiome (PC1,PC2)
```{r, cache=TRUE, echo=FALSE}
p <- ggplot(pc_scores, aes(x = PC1, y = PC2, color = microbiome, shape = strain, text = rownames(pc_scores))) +
geom_point() +
labs(title = "PCA Plot") +
xlab(str_glue("PC1, {round(pca$variance[1],2)}%")) +
ylab(str_glue("PC2, {round(pca$variance[2],2)}%")) +
theme(plot.title = element_text(size = 20))

ggplotly(p, tooltip = "text")
```
## Microbiome (PC2,PC3)
```{r, echo=FALSE}
p <- ggplot(pc_scores, aes(x = PC2, y = PC3, color = microbiome, shape = strain, text = rownames(pc_scores))) +
geom_point() +
labs(title = "PCA Plot") +
xlab(str_glue("PC2, {round(pca$variance[2],2)}%")) +
ylab(str_glue("PC3, {round(pca$variance[3],2)}%")) +
theme(plot.title = element_text(size = 20))

ggplotly(p, tooltip = "text")
```
## Age (PC1,PC2)
```{r, cache=TRUE,echo=FALSE}
p <- ggplot(pc_scores, aes(x = PC1, y = PC2, color = age, shape = strain, text = rownames(pc_scores))) +
geom_point() +
labs(title = "PCA Plot") +
xlab(str_glue("PC1, {round(pca$variance[1],2)}%")) +
ylab(str_glue("PC2, {round(pca$variance[2],2)}%")) +
theme(plot.title = element_text(size = 20))

ggplotly(p, tooltip = "text")
```
## Age (PC2,PC3)
```{r, cache=TRUE,echo=FALSE}
p <- ggplot(pc_scores, aes(x = PC2, y = PC3, color = age, shape = strain, text = rownames(pc_scores))) +
geom_point() +
labs(title = "PCA Plot") +
xlab(str_glue("PC2, {round(pca$variance[2],2)}%")) +
ylab(str_glue("PC3, {round(pca$variance[3],2)}%")) +
theme(plot.title = element_text(size = 20))

ggplotly(p, tooltip = "text")
```
## Batch (PC1,PC2)
```{r, cache=TRUE,echo=FALSE}
p <- ggplot(pc_scores, aes(x = PC1, y = PC2, color = batch, shape = strain, text = rownames(pc_scores))) +
geom_point() +
labs(title = "PCA Plot") +
xlab(str_glue("PC1, {round(pca$variance[1],2)}%")) +
ylab(str_glue("PC2, {round(pca$variance[2],2)}%")) +
theme(plot.title = element_text(size = 20))

ggplotly(p, tooltip = "text")
```
## Batch (PC2,PC3)
```{r, cache=TRUE,echo=FALSE}
p <- ggplot(pc_scores, aes(x = PC2, y = PC3, color = batch, shape = strain, text = rownames(pc_scores))) +
geom_point() +
labs(title = "PCA Plot") +
xlab(str_glue("PC2, {round(pca$variance[2],2)}%")) +
ylab(str_glue("PC3, {round(pca$variance[3],2)}%")) +
theme(plot.title = element_text(size = 20))

ggplotly(p, tooltip = "text")
```
:::

## Complete Cases Liver (without liv_4402)
:::: {.panel-tabset}

## All Strains
::: {.panel-tabset}
### Microbiome (PC1,PC2)
```{r, cache=TRUE, echo=FALSE}
pca <- trqwe::mcreadRDS(here("results","rds","PCA","pca_75_liver_cc.rds"), mc.cores = 4)
pc_scores <- pca$rotated %>% as.data.frame
pc_scores$microbiome <- pca$metadata$microbiome
pc_scores$age <- pca$metadata$age
pc_scores$organ <- pca$metadata$organ
pc_scores$batch <- pca$metadata$batch
pc_scores$strain <-  pca$metadata$strain
p <- ggplot(pc_scores, aes(x = PC1, y = PC2, color = microbiome, shape = strain, text = rownames(pc_scores))) +
geom_point() +
labs(title = "PCA Plot") +
xlab(str_glue("PC1, {round(pca$variance[1],2)}%")) +
ylab(str_glue("PC2, {round(pca$variance[2],2)}%")) +
theme(plot.title = element_text(size = 20))

ggplotly(p, tooltip = "text")
```
### Microbiome (PC2,PC3)
```{r, echo=FALSE}
p <- ggplot(pc_scores, aes(x = PC2, y = PC3, color = microbiome, shape = strain, text = rownames(pc_scores))) +
geom_point() +
labs(title = "PCA Plot") +
xlab(str_glue("PC2, {round(pca$variance[2],2)}%")) +
ylab(str_glue("PC3, {round(pca$variance[3],2)}%")) +
theme(plot.title = element_text(size = 20))

ggplotly(p, tooltip = "text")
```
### Age (PC1,PC2)
```{r, cache=TRUE,echo=FALSE}
p <- ggplot(pc_scores, aes(x = PC1, y = PC2, color = age, shape = strain, text = rownames(pc_scores))) +
geom_point() +
labs(title = "PCA Plot") +
xlab(str_glue("PC1, {round(pca$variance[1],2)}%")) +
ylab(str_glue("PC2, {round(pca$variance[2],2)}%")) +
theme(plot.title = element_text(size = 20))

ggplotly(p, tooltip = "text")
```
### Age (PC2,PC3)
```{r, cache=TRUE,echo=FALSE}
p <- ggplot(pc_scores, aes(x = PC2, y = PC3, color = age, shape = strain, text = rownames(pc_scores))) +
geom_point() +
labs(title = "PCA Plot") +
xlab(str_glue("PC2, {round(pca$variance[2],2)}%")) +
ylab(str_glue("PC3, {round(pca$variance[3],2)}%")) +
theme(plot.title = element_text(size = 20))

ggplotly(p, tooltip = "text")
```
### Batch (PC1,PC2)
```{r, cache=TRUE,echo=FALSE}
p <- ggplot(pc_scores, aes(x = PC1, y = PC2, color = batch, shape = strain, text = rownames(pc_scores))) +
geom_point() +
labs(title = "PCA Plot") +
xlab(str_glue("PC1, {round(pca$variance[1],2)}%")) +
ylab(str_glue("PC2, {round(pca$variance[2],2)}%")) +
theme(plot.title = element_text(size = 20))

ggplotly(p, tooltip = "text")
```
### Batch (PC2,PC3)
```{r, cache=TRUE,echo=FALSE}
p <- ggplot(pc_scores, aes(x = PC2, y = PC3, color = batch, shape = strain, text = rownames(pc_scores))) +
geom_point() +
labs(title = "PCA Plot") +
xlab(str_glue("PC2, {round(pca$variance[2],2)}%")) +
ylab(str_glue("PC3, {round(pca$variance[3],2)}%")) +
theme(plot.title = element_text(size = 20))

ggplotly(p, tooltip = "text")
```
:::

## C57BL6
::: {.panel-tabset}
### Microbiome (PC1,PC2)
```{r, cache=TRUE, echo=FALSE}
pca <- trqwe::mcreadRDS(here("results","rds","PCA","pca_75_liver_bl6_cc.rds"), mc.cores = 4)
pc_scores <- pca$rotated %>% as.data.frame
pc_scores$microbiome <- pca$metadata$microbiome
pc_scores$age <- pca$metadata$age
pc_scores$organ <- pca$metadata$organ
pc_scores$batch <- pca$metadata$batch
pc_scores$strain <-  pca$metadata$strain
p <- ggplot(pc_scores, aes(x = PC1, y = PC2, color = microbiome, text = rownames(pc_scores))) +
geom_point() +
labs(title = "PCA Plot") +
xlab(str_glue("PC1, {round(pca$variance[1],2)}%")) +
ylab(str_glue("PC2, {round(pca$variance[2],2)}%")) +
theme(plot.title = element_text(size = 20))

ggplotly(p, tooltip = "text")
```
### Microbiome (PC2,PC3)
```{r, echo=FALSE}
p <- ggplot(pc_scores, aes(x = PC2, y = PC3, color = microbiome, text = rownames(pc_scores))) +
geom_point() +
labs(title = "PCA Plot") +
xlab(str_glue("PC2, {round(pca$variance[2],2)}%")) +
ylab(str_glue("PC3, {round(pca$variance[3],2)}%")) +
theme(plot.title = element_text(size = 20))

ggplotly(p, tooltip = "text")
```
### Age (PC1,PC2)
```{r, cache=TRUE,echo=FALSE}
p <- ggplot(pc_scores, aes(x = PC1, y = PC2, color = age, shape = microbiome, text = rownames(pc_scores))) +
geom_point() +
labs(title = "PCA Plot") +
xlab(str_glue("PC1, {round(pca$variance[1],2)}%")) +
ylab(str_glue("PC2, {round(pca$variance[2],2)}%")) +
theme(plot.title = element_text(size = 20))

ggplotly(p, tooltip = "text")
```
### Age (PC2,PC3)
```{r, cache=TRUE,echo=FALSE}
p <- ggplot(pc_scores, aes(x = PC2, y = PC3, color = age, shape = microbiome, text = rownames(pc_scores))) +
geom_point() +
labs(title = "PCA Plot") +
xlab(str_glue("PC2, {round(pca$variance[2],2)}%")) +
ylab(str_glue("PC3, {round(pca$variance[3],2)}%")) +
theme(plot.title = element_text(size = 20)) +
NULL


ggplotly(p, tooltip = "text")
```
### Batch (PC1,PC2)
```{r, cache=TRUE,echo=FALSE}
p <- ggplot(pc_scores, aes(x = PC1, y = PC2, color = batch, shape = microbiome, text = rownames(pc_scores))) +
geom_point() +
labs(title = "PCA Plot") +
xlab(str_glue("PC1, {round(pca$variance[1],2)}%")) +
ylab(str_glue("PC2, {round(pca$variance[2],2)}%")) +
theme(plot.title = element_text(size = 20))

ggplotly(p, tooltip = "text")
```
### Batch (PC2,PC3)
```{r, cache=TRUE,echo=FALSE}
p <- ggplot(pc_scores, aes(x = PC2, y = PC3, color = batch, shape = microbiome, text = rownames(pc_scores))) +
geom_point() +
labs(title = "PCA Plot") +
xlab(str_glue("PC2, {round(pca$variance[2],2)}%")) +
ylab(str_glue("PC3, {round(pca$variance[3],2)}%")) +
theme(plot.title = element_text(size = 20))

ggplotly(p, tooltip = "text")
```
:::

## 129SVEV
::: {.panel-tabset}
### Microbiome (PC1,PC2)
```{r, cache=TRUE, echo=FALSE}
pca <- trqwe::mcreadRDS(here("results","rds","PCA","pca_75_liver_129_cc.rds"), mc.cores = 4)
pc_scores <- pca$rotated %>% as.data.frame
pc_scores$microbiome <- pca$metadata$microbiome
pc_scores$age <- pca$metadata$age
pc_scores$organ <- pca$metadata$organ
pc_scores$batch <- pca$metadata$batch
pc_scores$strain <-  pca$metadata$strain
p <- ggplot(pc_scores, aes(x = PC1, y = PC2, color = microbiome, text = rownames(pc_scores))) +
geom_point() +
labs(title = "PCA Plot") +
xlab(str_glue("PC1, {round(pca$variance[1],2)}%")) +
ylab(str_glue("PC2, {round(pca$variance[2],2)}%")) +
theme(plot.title = element_text(size = 20))

ggplotly(p, tooltip = "text")
```
### Microbiome (PC2,PC3)
```{r, echo=FALSE}
p <- ggplot(pc_scores, aes(x = PC2, y = PC3, color = microbiome, text = rownames(pc_scores))) +
geom_point() +
labs(title = "PCA Plot") +
xlab(str_glue("PC2, {round(pca$variance[2],2)}%")) +
ylab(str_glue("PC3, {round(pca$variance[3],2)}%")) +
theme(plot.title = element_text(size = 20))

ggplotly(p, tooltip = "text")
```
### Age (PC1,PC2)
```{r, cache=TRUE,echo=FALSE}
p <- ggplot(pc_scores, aes(x = PC1, y = PC2, color = age, shape = microbiome, text = rownames(pc_scores))) +
geom_point() +
labs(title = "PCA Plot") +
xlab(str_glue("PC1, {round(pca$variance[1],2)}%")) +
ylab(str_glue("PC2, {round(pca$variance[2],2)}%")) +
theme(plot.title = element_text(size = 20))

ggplotly(p, tooltip = "text")
```
### Age (PC2,PC3)
```{r, cache=TRUE,echo=FALSE}
p <- ggplot(pc_scores, aes(x = PC2, y = PC3, color = age, shape = microbiome, text = rownames(pc_scores))) +
geom_point() +
labs(title = "PCA Plot") +
xlab(str_glue("PC2, {round(pca$variance[2],2)}%")) +
ylab(str_glue("PC3, {round(pca$variance[3],2)}%")) +
theme(plot.title = element_text(size = 20))

ggplotly(p, tooltip = "text")
```
### Batch (PC1,PC2)
```{r, cache=TRUE,echo=FALSE}
p <- ggplot(pc_scores, aes(x = PC1, y = PC2, color = batch, shape = microbiome, text = rownames(pc_scores))) +
geom_point() +
labs(title = "PCA Plot") +
xlab(str_glue("PC1, {round(pca$variance[1],2)}%")) +
ylab(str_glue("PC2, {round(pca$variance[2],2)}%")) +
theme(plot.title = element_text(size = 20))

ggplotly(p, tooltip = "text")
```
### Batch (PC2,PC3)
```{r, cache=TRUE,echo=FALSE}
p <- ggplot(pc_scores, aes(x = PC2, y = PC3, color = batch, shape = microbiome, text = rownames(pc_scores))) +
geom_point() +
labs(title = "PCA Plot") +
xlab(str_glue("PC2, {round(pca$variance[2],2)}%")) +
ylab(str_glue("PC3, {round(pca$variance[3],2)}%")) +
theme(plot.title = element_text(size = 20))

ggplotly(p, tooltip = "text")
```
:::

::::

 
## Complete Cases Spleen
:::: {.panel-tabset}

## All Strains
::: {.panel-tabset}
### Microbiome (PC1,PC2)
```{r, cache=TRUE, echo=FALSE}
pca <- trqwe::mcreadRDS(here("results","rds","PCA","pca_75_spleen_cc.rds"), mc.cores = 4)
pc_scores <- pca$rotated %>% as.data.frame
pc_scores$microbiome <- pca$metadata$microbiome
pc_scores$age <- pca$metadata$age
pc_scores$organ <- pca$metadata$organ
pc_scores$batch <- pca$metadata$batch
pc_scores$strain <-  pca$metadata$strain
p <- ggplot(pc_scores, aes(x = PC1, y = PC2, color = microbiome, shape = strain, text = rownames(pc_scores))) +
geom_point() +
labs(title = "PCA Plot") +
xlab(str_glue("PC1, {round(pca$variance[1],2)}%")) +
ylab(str_glue("PC2, {round(pca$variance[2],2)}%")) +
theme(plot.title = element_text(size = 20))

ggplotly(p, tooltip = "text")
```
### Microbiome (PC2,PC3)
```{r, echo=FALSE}
p <- ggplot(pc_scores, aes(x = PC2, y = PC3, color = microbiome, shape = strain, text = rownames(pc_scores))) +
geom_point() +
labs(title = "PCA Plot") +
xlab(str_glue("PC2, {round(pca$variance[2],2)}%")) +
ylab(str_glue("PC3, {round(pca$variance[3],2)}%")) +
theme(plot.title = element_text(size = 20))

ggplotly(p, tooltip = "text")
```
### Age (PC1,PC2)
```{r, cache=TRUE,echo=FALSE}
p <- ggplot(pc_scores, aes(x = PC1, y = PC2, color = age, shape = strain, text = rownames(pc_scores))) +
geom_point() +
labs(title = "PCA Plot") +
xlab(str_glue("PC1, {round(pca$variance[1],2)}%")) +
ylab(str_glue("PC2, {round(pca$variance[2],2)}%")) +
theme(plot.title = element_text(size = 20))

ggplotly(p, tooltip = "text")
```
### Age (PC2,PC3)
```{r, cache=TRUE,echo=FALSE}
p <- ggplot(pc_scores, aes(x = PC2, y = PC3, color = age, shape = strain, text = rownames(pc_scores))) +
geom_point() +
labs(title = "PCA Plot") +
xlab(str_glue("PC2, {round(pca$variance[2],2)}%")) +
ylab(str_glue("PC3, {round(pca$variance[3],2)}%")) +
theme(plot.title = element_text(size = 20))

ggplotly(p, tooltip = "text")
```
### Batch (PC1,PC2)
```{r, cache=TRUE,echo=FALSE}
p <- ggplot(pc_scores, aes(x = PC1, y = PC2, color = batch, shape = strain, text = rownames(pc_scores))) +
geom_point() +
labs(title = "PCA Plot") +
xlab(str_glue("PC1, {round(pca$variance[1],2)}%")) +
ylab(str_glue("PC2, {round(pca$variance[2],2)}%")) +
theme(plot.title = element_text(size = 20))

ggplotly(p, tooltip = "text")
```
### Batch (PC2,PC3)
```{r, cache=TRUE,echo=FALSE}
p <- ggplot(pc_scores, aes(x = PC2, y = PC3, color = batch, shape = strain, text = rownames(pc_scores))) +
geom_point() +
labs(title = "PCA Plot") +
xlab(str_glue("PC2, {round(pca$variance[2],2)}%")) +
ylab(str_glue("PC3, {round(pca$variance[3],2)}%")) +
theme(plot.title = element_text(size = 20))

ggplotly(p, tooltip = "text")
```
:::

## C57BL6
::: {.panel-tabset}
### Microbiome (PC1,PC2)
```{r, cache=TRUE, echo=FALSE}
pca <- trqwe::mcreadRDS(here("results","rds","PCA","pca_75_spleen_bl6_cc.rds"), mc.cores = 4)
pc_scores <- pca$rotated %>% as.data.frame
pc_scores$microbiome <- pca$metadata$microbiome
pc_scores$age <- pca$metadata$age
pc_scores$organ <- pca$metadata$organ
pc_scores$batch <- pca$metadata$batch
pc_scores$strain <-  pca$metadata$strain
p <- ggplot(pc_scores, aes(x = PC1, y = PC2, color = microbiome, text = rownames(pc_scores))) +
geom_point() +
labs(title = "PCA Plot") +
xlab(str_glue("PC1, {round(pca$variance[1],2)}%")) +
ylab(str_glue("PC2, {round(pca$variance[2],2)}%")) +
theme(plot.title = element_text(size = 20))

ggplotly(p, tooltip = "text")
```
### Microbiome (PC2,PC3)
```{r, echo=FALSE}
p <- ggplot(pc_scores, aes(x = PC2, y = PC3, color = microbiome, text = rownames(pc_scores))) +
geom_point() +
labs(title = "PCA Plot") +
xlab(str_glue("PC2, {round(pca$variance[2],2)}%")) +
ylab(str_glue("PC3, {round(pca$variance[3],2)}%")) +
theme(plot.title = element_text(size = 20))

ggplotly(p, tooltip = "text")
```
### Age (PC1,PC2)
```{r, cache=TRUE,echo=FALSE}
p <- ggplot(pc_scores, aes(x = PC1, y = PC2, color = age, shape = microbiome, text = rownames(pc_scores))) +
geom_point() +
labs(title = "PCA Plot") +
xlab(str_glue("PC1, {round(pca$variance[1],2)}%")) +
ylab(str_glue("PC2, {round(pca$variance[2],2)}%")) +
theme(plot.title = element_text(size = 20))

ggplotly(p, tooltip = "text")
```
### Age (PC2,PC3)
```{r, cache=TRUE,echo=FALSE}
p <- ggplot(pc_scores, aes(x = PC2, y = PC3, color = age, shape = microbiome, text = rownames(pc_scores))) +
geom_point() +
labs(title = "PCA Plot") +
xlab(str_glue("PC2, {round(pca$variance[2],2)}%")) +
ylab(str_glue("PC3, {round(pca$variance[3],2)}%")) +
theme(plot.title = element_text(size = 20))

ggplotly(p, tooltip = "text")
```
### Batch (PC1,PC2)
```{r, cache=TRUE,echo=FALSE}
p <- ggplot(pc_scores, aes(x = PC1, y = PC2, color = batch, shape = microbiome, text = rownames(pc_scores))) +
geom_point() +
labs(title = "PCA Plot") +
xlab(str_glue("PC1, {round(pca$variance[1],2)}%")) +
ylab(str_glue("PC2, {round(pca$variance[2],2)}%")) +
theme(plot.title = element_text(size = 20))

ggplotly(p, tooltip = "text")
```
### Batch (PC2,PC3)
```{r, cache=TRUE,echo=FALSE}
p <- ggplot(pc_scores, aes(x = PC2, y = PC3, color = batch, shape = microbiome, text = rownames(pc_scores))) +
geom_point() +
labs(title = "PCA Plot") +
xlab(str_glue("PC2, {round(pca$variance[2],2)}%")) +
ylab(str_glue("PC3, {round(pca$variance[3],2)}%")) +
theme(plot.title = element_text(size = 20))

ggplotly(p, tooltip = "text")
```
:::

## 129SVEV
::: {.panel-tabset}
### Microbiome (PC1,PC2)
```{r, cache=TRUE, echo=FALSE}
pca <- trqwe::mcreadRDS(here("results","rds","PCA","pca_75_spleen_129_cc.rds"), mc.cores = 4)
pc_scores <- pca$rotated %>% as.data.frame
pc_scores$microbiome <- pca$metadata$microbiome
pc_scores$age <- pca$metadata$age
pc_scores$organ <- pca$metadata$organ
pc_scores$batch <- pca$metadata$batch
pc_scores$strain <-  pca$metadata$strain
p <- ggplot(pc_scores, aes(x = PC1, y = PC2, color = microbiome, text = rownames(pc_scores))) +
geom_point() +
labs(title = "PCA Plot") +
xlab(str_glue("PC1, {round(pca$variance[1],2)}%")) +
ylab(str_glue("PC2, {round(pca$variance[2],2)}%")) +
theme(plot.title = element_text(size = 20))

ggplotly(p, tooltip = "text")
```
### Microbiome (PC2,PC3)
```{r, echo=FALSE}
p <- ggplot(pc_scores, aes(x = PC2, y = PC3, color = microbiome, text = rownames(pc_scores))) +
geom_point() +
labs(title = "PCA Plot") +
xlab(str_glue("PC2, {round(pca$variance[2],2)}%")) +
ylab(str_glue("PC3, {round(pca$variance[3],2)}%")) +
theme(plot.title = element_text(size = 20))

ggplotly(p, tooltip = "text")
```
### Age (PC1,PC2)
```{r, cache=TRUE,echo=FALSE}
p <- ggplot(pc_scores, aes(x = PC1, y = PC2, color = age, shape = microbiome, text = rownames(pc_scores))) +
geom_point() +
labs(title = "PCA Plot") +
xlab(str_glue("PC1, {round(pca$variance[1],2)}%")) +
ylab(str_glue("PC2, {round(pca$variance[2],2)}%")) +
theme(plot.title = element_text(size = 20))

ggplotly(p, tooltip = "text")
```
### Age (PC2,PC3)
```{r, cache=TRUE,echo=FALSE}
p <- ggplot(pc_scores, aes(x = PC2, y = PC3, color = age, shape = microbiome, text = rownames(pc_scores))) +
geom_point() +
labs(title = "PCA Plot") +
xlab(str_glue("PC2, {round(pca$variance[2],2)}%")) +
ylab(str_glue("PC3, {round(pca$variance[3],2)}%")) +
theme(plot.title = element_text(size = 20))

ggplotly(p, tooltip = "text")
```
### Batch (PC1,PC2)
```{r, cache=TRUE,echo=FALSE}
p <- ggplot(pc_scores, aes(x = PC1, y = PC2, color = batch, shape = microbiome, text = rownames(pc_scores))) +
geom_point() +
labs(title = "PCA Plot") +
xlab(str_glue("PC1, {round(pca$variance[1],2)}%")) +
ylab(str_glue("PC2, {round(pca$variance[2],2)}%")) +
theme(plot.title = element_text(size = 20))

ggplotly(p, tooltip = "text")
```
### Batch (PC2,PC3)
```{r, cache=TRUE,echo=FALSE}
p <- ggplot(pc_scores, aes(x = PC2, y = PC3, color = batch, shape = microbiome, text = rownames(pc_scores))) +
geom_point() +
labs(title = "PCA Plot") +
xlab(str_glue("PC2, {round(pca$variance[2],2)}%")) +
ylab(str_glue("PC3, {round(pca$variance[3],2)}%")) +
theme(plot.title = element_text(size = 20))

ggplotly(p, tooltip = "text")
```
:::

::::


## Complete Cases Colon
:::: {.panel-tabset}

## All Strains
::: {.panel-tabset}
### Organ (PC1,PC2)
```{r, cache=TRUE, echo=FALSE}
pca <- trqwe::mcreadRDS(here("results","rds","PCA","pca_75_colon_cc.rds"), mc.cores = 4)
pc_scores <- pca$rotated %>% as.data.frame
pc_scores$microbiome <- pca$metadata$microbiome
pc_scores$age <- pca$metadata$age
pc_scores$organ <- pca$metadata$organ
pc_scores$batch <- pca$metadata$batch
pc_scores$strain <-  pca$metadata$strain
p <- ggplot(pc_scores, aes(x = PC1, y = PC2, color = organ, shape = strain, text = rownames(pc_scores))) +
geom_point() +
labs(title = "PCA Plot") +
xlab(str_glue("PC1, {round(pca$variance[1],2)}%")) +
ylab(str_glue("PC2, {round(pca$variance[2],2)}%")) +
theme(plot.title = element_text(size = 20))

ggplotly(p, tooltip = "text")
```
### Organ (PC2,PC3)
```{r, cache=TRUE, echo=FALSE}
p <- ggplot(pc_scores, aes(x = PC2, y = PC3, color = organ, shape = strain, text = rownames(pc_scores))) +
geom_point() +
labs(title = "PCA Plot") +
xlab(str_glue("PC2, {round(pca$variance[2],2)}%")) +
ylab(str_glue("PC3, {round(pca$variance[3],2)}%")) +
theme(plot.title = element_text(size = 20))

ggplotly(p, tooltip = "text")
```
### Microbiome (PC1,PC2)
```{r, cache=TRUE, echo=FALSE}
p <- ggplot(pc_scores, aes(x = PC1, y = PC2, color = microbiome, shape = strain, text = rownames(pc_scores))) +
geom_point() +
labs(title = "PCA Plot") +
xlab(str_glue("PC1, {round(pca$variance[1],2)}%")) +
ylab(str_glue("PC2, {round(pca$variance[2],2)}%")) +
theme(plot.title = element_text(size = 20))

ggplotly(p, tooltip = "text")
```
### Microbiome (PC2,PC3)
```{r, echo=FALSE}
p <- ggplot(pc_scores, aes(x = PC2, y = PC3, color = microbiome, shape = strain, text = rownames(pc_scores))) +
geom_point() +
labs(title = "PCA Plot") +
xlab(str_glue("PC2, {round(pca$variance[2],2)}%")) +
ylab(str_glue("PC3, {round(pca$variance[3],2)}%")) +
theme(plot.title = element_text(size = 20))

ggplotly(p, tooltip = "text")
```
### Age (PC1,PC2)
```{r, cache=TRUE,echo=FALSE}
p <- ggplot(pc_scores, aes(x = PC1, y = PC2, color = age, shape = strain, text = rownames(pc_scores))) +
geom_point() +
labs(title = "PCA Plot") +
xlab(str_glue("PC1, {round(pca$variance[1],2)}%")) +
ylab(str_glue("PC2, {round(pca$variance[2],2)}%")) +
theme(plot.title = element_text(size = 20))

ggplotly(p, tooltip = "text")
```
### Age (PC2,PC3)
```{r, cache=TRUE,echo=FALSE}
p <- ggplot(pc_scores, aes(x = PC2, y = PC3, color = age, shape = strain, text = rownames(pc_scores))) +
geom_point() +
labs(title = "PCA Plot") +
xlab(str_glue("PC2, {round(pca$variance[2],2)}%")) +
ylab(str_glue("PC3, {round(pca$variance[3],2)}%")) +
theme(plot.title = element_text(size = 20))

ggplotly(p, tooltip = "text")
```
### Batch (PC1,PC2)
```{r, cache=TRUE,echo=FALSE}
p <- ggplot(pc_scores, aes(x = PC1, y = PC2, color = batch, shape = strain, text = rownames(pc_scores))) +
geom_point() +
labs(title = "PCA Plot") +
xlab(str_glue("PC1, {round(pca$variance[1],2)}%")) +
ylab(str_glue("PC2, {round(pca$variance[2],2)}%")) +
theme(plot.title = element_text(size = 20))

ggplotly(p, tooltip = "text")
```
### Batch (PC2,PC3)
```{r, cache=TRUE,echo=FALSE}
p <- ggplot(pc_scores, aes(x = PC2, y = PC3, color = batch, shape = strain, text = rownames(pc_scores))) +
geom_point() +
labs(title = "PCA Plot") +
xlab(str_glue("PC2, {round(pca$variance[2],2)}%")) +
ylab(str_glue("PC3, {round(pca$variance[3],2)}%")) +
theme(plot.title = element_text(size = 20))

ggplotly(p, tooltip = "text")
```
:::

## C57BL6
::: {.panel-tabset}
### Organ (PC1,PC2)
```{r, cache=TRUE, echo=FALSE}
pca <- trqwe::mcreadRDS(here("results","rds","PCA","pca_75_colon_bl6_cc.rds"), mc.cores = 4)
pc_scores <- pca$rotated %>% as.data.frame
pc_scores$microbiome <- pca$metadata$microbiome
pc_scores$age <- pca$metadata$age
pc_scores$organ <- pca$metadata$organ
pc_scores$batch <- pca$metadata$batch
pc_scores$strain <-  pca$metadata$strain
p <- ggplot(pc_scores, aes(x = PC1, y = PC2, color = organ, shape = microbiome, text = rownames(pc_scores))) +
geom_point() +
labs(title = "PCA Plot") +
xlab(str_glue("PC1, {round(pca$variance[1],2)}%")) +
ylab(str_glue("PC2, {round(pca$variance[2],2)}%")) +
theme(plot.title = element_text(size = 20))

ggplotly(p, tooltip = "text")
```
### Organ (PC2,PC3)
```{r, cache=TRUE, echo=FALSE}
p <- ggplot(pc_scores, aes(x = PC2, y = PC3, color = organ, shape = microbiome, text = rownames(pc_scores))) +
geom_point() +
labs(title = "PCA Plot") +
xlab(str_glue("PC2, {round(pca$variance[2],2)}%")) +
ylab(str_glue("PC3, {round(pca$variance[3],2)}%")) +
theme(plot.title = element_text(size = 20))

ggplotly(p, tooltip = "text")
```
### Microbiome (PC1,PC2)
```{r, cache=TRUE, echo=FALSE}
p <- ggplot(pc_scores, aes(x = PC1, y = PC2, color = microbiome, text = rownames(pc_scores))) +
geom_point() +
labs(title = "PCA Plot") +
xlab(str_glue("PC1, {round(pca$variance[1],2)}%")) +
ylab(str_glue("PC2, {round(pca$variance[2],2)}%")) +
theme(plot.title = element_text(size = 20))

ggplotly(p, tooltip = "text")
```
### Microbiome (PC2,PC3)
```{r, echo=FALSE}
p <- ggplot(pc_scores, aes(x = PC2, y = PC3, color = microbiome, text = rownames(pc_scores))) +
geom_point() +
labs(title = "PCA Plot") +
xlab(str_glue("PC2, {round(pca$variance[2],2)}%")) +
ylab(str_glue("PC3, {round(pca$variance[3],2)}%")) +
theme(plot.title = element_text(size = 20))

ggplotly(p, tooltip = "text")
```
### Age (PC1,PC2)
```{r, cache=TRUE,echo=FALSE}
p <- ggplot(pc_scores, aes(x = PC1, y = PC2, color = age, shape = microbiome, text = rownames(pc_scores))) +
geom_point() +
labs(title = "PCA Plot") +
xlab(str_glue("PC1, {round(pca$variance[1],2)}%")) +
ylab(str_glue("PC2, {round(pca$variance[2],2)}%")) +
theme(plot.title = element_text(size = 20))

ggplotly(p, tooltip = "text")
```
### Age (PC2,PC3)
```{r, cache=TRUE,echo=FALSE}
p <- ggplot(pc_scores, aes(x = PC2, y = PC3, color = age, shape = microbiome, text = rownames(pc_scores))) +
geom_point() +
labs(title = "PCA Plot") +
xlab(str_glue("PC2, {round(pca$variance[2],2)}%")) +
ylab(str_glue("PC3, {round(pca$variance[3],2)}%")) +
theme(plot.title = element_text(size = 20))

ggplotly(p, tooltip = "text")
```
### Batch (PC1,PC2)
```{r, cache=TRUE,echo=FALSE}
p <- ggplot(pc_scores, aes(x = PC1, y = PC2, color = batch, shape = microbiome, text = rownames(pc_scores))) +
geom_point() +
labs(title = "PCA Plot") +
xlab(str_glue("PC1, {round(pca$variance[1],2)}%")) +
ylab(str_glue("PC2, {round(pca$variance[2],2)}%")) +
theme(plot.title = element_text(size = 20))

ggplotly(p, tooltip = "text")
```
### Batch (PC2,PC3)
```{r, cache=TRUE,echo=FALSE}
p <- ggplot(pc_scores, aes(x = PC2, y = PC3, color = batch, shape = microbiome, text = rownames(pc_scores))) +
geom_point() +
labs(title = "PCA Plot") +
xlab(str_glue("PC2, {round(pca$variance[2],2)}%")) +
ylab(str_glue("PC3, {round(pca$variance[3],2)}%")) +
theme(plot.title = element_text(size = 20))

ggplotly(p, tooltip = "text")
```
:::

## 129SVEV
::: {.panel-tabset}
### Organ (PC1,PC2)
```{r, cache=TRUE, echo=FALSE}
pca <- trqwe::mcreadRDS(here("results","rds","PCA","pca_75_colon_129_cc.rds"), mc.cores = 4)
pc_scores <- pca$rotated %>% as.data.frame
pc_scores$microbiome <- pca$metadata$microbiome
pc_scores$age <- pca$metadata$age
pc_scores$organ <- pca$metadata$organ
pc_scores$batch <- pca$metadata$batch
pc_scores$strain <-  pca$metadata$strain
p <- ggplot(pc_scores, aes(x = PC1, y = PC2, color = organ, shape = microbiome, text = rownames(pc_scores))) +
geom_point() +
labs(title = "PCA Plot") +
xlab(str_glue("PC1, {round(pca$variance[1],2)}%")) +
ylab(str_glue("PC2, {round(pca$variance[2],2)}%")) +
theme(plot.title = element_text(size = 20))

ggplotly(p, tooltip = "text")
```
### Organ (PC2,PC3)
```{r, cache=TRUE, echo=FALSE}
p <- ggplot(pc_scores, aes(x = PC2, y = PC3, color = organ, shape = microbiome, text = rownames(pc_scores))) +
geom_point() +
labs(title = "PCA Plot") +
xlab(str_glue("PC2, {round(pca$variance[2],2)}%")) +
ylab(str_glue("PC3, {round(pca$variance[3],2)}%")) +
theme(plot.title = element_text(size = 20))

ggplotly(p, tooltip = "text")
```
### Microbiome (PC1,PC2)
```{r, cache=TRUE, echo=FALSE}
p <- ggplot(pc_scores, aes(x = PC1, y = PC2, color = microbiome, text = rownames(pc_scores))) +
geom_point() +
labs(title = "PCA Plot") +
xlab(str_glue("PC1, {round(pca$variance[1],2)}%")) +
ylab(str_glue("PC2, {round(pca$variance[2],2)}%")) +
theme(plot.title = element_text(size = 20))

ggplotly(p, tooltip = "text")
```
### Microbiome (PC2,PC3)
```{r, echo=FALSE}
p <- ggplot(pc_scores, aes(x = PC2, y = PC3, color = microbiome, text = rownames(pc_scores))) +
geom_point() +
labs(title = "PCA Plot") +
xlab(str_glue("PC2, {round(pca$variance[2],2)}%")) +
ylab(str_glue("PC3, {round(pca$variance[3],2)}%")) +
theme(plot.title = element_text(size = 20))

ggplotly(p, tooltip = "text")
```
### Age (PC1,PC2)
```{r, cache=TRUE,echo=FALSE}
p <- ggplot(pc_scores, aes(x = PC1, y = PC2, color = age, shape = microbiome, text = rownames(pc_scores))) +
geom_point() +
labs(title = "PCA Plot") +
xlab(str_glue("PC1, {round(pca$variance[1],2)}%")) +
ylab(str_glue("PC2, {round(pca$variance[2],2)}%")) +
theme(plot.title = element_text(size = 20))

ggplotly(p, tooltip = "text")
```
### Age (PC2,PC3)
```{r, cache=TRUE,echo=FALSE}
p <- ggplot(pc_scores, aes(x = PC2, y = PC3, color = age, shape = microbiome, text = rownames(pc_scores))) +
geom_point() +
labs(title = "PCA Plot") +
xlab(str_glue("PC2, {round(pca$variance[2],2)}%")) +
ylab(str_glue("PC3, {round(pca$variance[3],2)}%")) +
theme(plot.title = element_text(size = 20))

ggplotly(p, tooltip = "text")
```
### Batch (PC1,PC2)
```{r, cache=TRUE,echo=FALSE}
p <- ggplot(pc_scores, aes(x = PC1, y = PC2, color = batch, shape = microbiome, text = rownames(pc_scores))) +
geom_point() +
labs(title = "PCA Plot") +
xlab(str_glue("PC1, {round(pca$variance[1],2)}%")) +
ylab(str_glue("PC2, {round(pca$variance[2],2)}%")) +
theme(plot.title = element_text(size = 20))

ggplotly(p, tooltip = "text")
```
### Batch (PC2,PC3)
```{r, cache=TRUE,echo=FALSE}
p <- ggplot(pc_scores, aes(x = PC2, y = PC3, color = batch, shape = microbiome, text = rownames(pc_scores))) +
geom_point() +
labs(title = "PCA Plot") +
xlab(str_glue("PC2, {round(pca$variance[2],2)}%")) +
ylab(str_glue("PC3, {round(pca$variance[3],2)}%")) +
theme(plot.title = element_text(size = 20))

ggplotly(p, tooltip = "text")
```
:::

::::


## Complete Cases Small Intestine
::: {.panel-tabset}
## Organ (PC1,PC2)
```{r, cache=TRUE, echo=FALSE}
pca <- trqwe::mcreadRDS(here("results","rds","PCA","pca_75_si_cc.rds"), mc.cores = 4)
pc_scores <- pca$rotated %>% as.data.frame
pc_scores$microbiome <- pca$metadata$microbiome
pc_scores$age <- pca$metadata$age
pc_scores$organ <- pca$metadata$organ
pc_scores$batch <- pca$metadata$batch
pc_scores$strain <-  pca$metadata$strain
p <- ggplot(pc_scores, aes(x = PC1, y = PC2, color = organ, shape = microbiome, text = rownames(pc_scores))) +
geom_point() +
labs(title = "PCA Plot") +
xlab(str_glue("PC1, {round(pca$variance[1],2)}%")) +
ylab(str_glue("PC2, {round(pca$variance[2],2)}%")) +
theme(plot.title = element_text(size = 20))

ggplotly(p, tooltip = "text")
```
## Organ (PC2,PC3)
```{r, cache=TRUE, echo=FALSE}
p <- ggplot(pc_scores, aes(x = PC2, y = PC3, color = organ, shape = microbiome, text = rownames(pc_scores))) +
geom_point() +
labs(title = "PCA Plot") +
xlab(str_glue("PC2, {round(pca$variance[2],2)}%")) +
ylab(str_glue("PC3, {round(pca$variance[3],2)}%")) +
theme(plot.title = element_text(size = 20))

ggplotly(p, tooltip = "text")
```
## Microbiome (PC1,PC2)
```{r, cache=TRUE, echo=FALSE}
p <- ggplot(pc_scores, aes(x = PC1, y = PC2, color = microbiome, text = rownames(pc_scores))) +
geom_point() +
labs(title = "PCA Plot") +
xlab(str_glue("PC1, {round(pca$variance[1],2)}%")) +
ylab(str_glue("PC2, {round(pca$variance[2],2)}%")) +
theme(plot.title = element_text(size = 20))

ggplotly(p, tooltip = "text")
```
## Microbiome (PC2,PC3)
```{r,echo=FALSE}
p <- ggplot(pc_scores, aes(x = PC2, y = PC3, color = microbiome, text = rownames(pc_scores))) +
geom_point() +
labs(title = "PCA Plot") +
xlab(str_glue("PC2, {round(pca$variance[2],2)}%")) +
ylab(str_glue("PC3, {round(pca$variance[3],2)}%")) +
theme(plot.title = element_text(size = 20))

ggplotly(p, tooltip = "text")
```
## Age (PC1,PC2)
```{r, cache=TRUE,echo=FALSE}
p <- ggplot(pc_scores, aes(x = PC1, y = PC2, color = age, shape = microbiome, text = rownames(pc_scores))) +
geom_point() +
labs(title = "PCA Plot") +
xlab(str_glue("PC1, {round(pca$variance[1],2)}%")) +
ylab(str_glue("PC2, {round(pca$variance[2],2)}%")) +
theme(plot.title = element_text(size = 20))

ggplotly(p, tooltip = "text")
```
## Age (PC2,PC3)
```{r, cache=TRUE,echo=FALSE}
p <- ggplot(pc_scores, aes(x = PC2, y = PC3, color = age, shape = microbiome, text = rownames(pc_scores))) +
geom_point() +
labs(title = "PCA Plot") +
xlab(str_glue("PC2, {round(pca$variance[2],2)}%")) +
ylab(str_glue("PC3, {round(pca$variance[3],2)}%")) +
theme(plot.title = element_text(size = 20))

ggplotly(p, tooltip = "text")
```
## Batch (PC1,PC2)
```{r, cache=TRUE,echo=FALSE}
p <- ggplot(pc_scores, aes(x = PC1, y = PC2, color = batch, shape = microbiome, text = rownames(pc_scores))) +
geom_point() +
labs(title = "PCA Plot") +
xlab(str_glue("PC1, {round(pca$variance[1],2)}%")) +
ylab(str_glue("PC2, {round(pca$variance[2],2)}%")) +
theme(plot.title = element_text(size = 20))

ggplotly(p, tooltip = "text")
```
## Batch (PC2,PC3)
```{r, cache=TRUE,echo=FALSE}
p <- ggplot(pc_scores, aes(x = PC2, y = PC3, color = batch, shape = microbiome, text = rownames(pc_scores))) +
geom_point() +
labs(title = "PCA Plot") +
xlab(str_glue("PC2, {round(pca$variance[2],2)}%")) +
ylab(str_glue("PC3, {round(pca$variance[3],2)}%")) +
theme(plot.title = element_text(size = 20))

ggplotly(p, tooltip = "text")
```
:::